---
title: "twitter_market_seg"
author: "Catherine Miao"
date: "8/10/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
mkt_seg = read.csv("/Users/CatherineMiao/Desktop/STA380-master/data/social_marketing.csv") %>% as.tbl
```

# Exploting Correlations between features 
```{r}
#install.packages("corrplot")
library(corrplot)
#str(mkt_seg)
cormp <- cor(mkt_seg[c(2:37)])

cex.before <- par("cex")
par(cex = 0.7)
corrplot(cormp, method ='shade',tl.cex = 0.65)
#par(cex = cex.before)

# strong corelation between personal fitness and health_nutrition 
# online gaming vs college_uni - 0.77
# travel vs politics - 0.66 
# beauty vs cooking - 0.66 
cor(mkt_seg$politics, mkt_seg$travel) # 0.66 
cor(mkt_seg$online_gaming, mkt_seg$college_uni) # 0.77
cor(mkt_seg$personal_fitness,mkt_seg$health_nutrition) #0.81
cor(mkt_seg$religion, mkt_seg$sports_fandom)

#cormp
#as.data.frame(apply(cormp, 2, function(x) ifelse (abs(x)>=0.6,x,"NA")))

```

```{r}
#summary(mkt_seg)
#names(mkt_seg)
raw_features = mkt_seg[-1]
features = scale(raw_features,center = T, scale = T)

mu = attr(features,"scaled:center")
sigma = attr(features,"scaled:scale")

#nrow(mkt_seg) #7882
#nrow(na.omit(mkt_seg))
kmeans=kmeans(features, 5)

#kmeans$center  # not super helpful
#kmeans$center[1,]*sigma + mu
#kmeans$center[2,]*sigma + mu
#kmeans$center[3,]*sigma + mu
#kmeans$center[4,]*sigma + mu
#kmeans$center[5,]*sigma + mu

#kmeans$size
#kmeans$cluster
```

# Finding Number of Clusters 
```{r}
library(foreach)
library(dplyr)
library(tidyverse)
mkt_seg = read.csv("/Users/CatherineMiao/Desktop/STA380-master/data/social_marketing.csv") %>% as.tbl
mkt_seg=na.omit(mkt_seg)
raw_features = mkt_seg[-1]
features = scale(raw_features,center = T, scale = T)
k_grid = seq(1,50, by=1)
SSE_grid = foreach(k=k_grid, .combine = "c") %do% {
   cluster_k = kmeans(features,k,nstart=5) 
   cluster_k$tot.withinss
 }


plot(k_grid, SSE_grid, xlim=c(0,20))

```

# CH Index - measure goodness of fit
# Find the K that maximize CH_grid 
```{r}
N=nrow(mkt_seg)
CH_grid = foreach(k=k_grid, .combine = "c") %do% {
   W = cluster_k$tot.withinss
   B = cluster_k$betweenss
   CH = (B/W)*((N-k)/(k-1))
   CH
 }
plot(k_grid, CH_grid)
```
From the within cluster sum-of-square plot and the CH index plot, we determine that the optimal number of clusters is between 2 and 15. We would like to use 5 as our number of clusters! 


# K-means clustering 
```{r}
plot(mkt_seg[c("outdoors","computers")],col=kmeans$cluster)

names(mkt_seg)

qplot(food, cooking, data=mkt_seg, color=factor(kmeans$cluster))

qplot(mkt_seg$online_gaming,mkt_seg$college_uni,color=factor(kmeans$cluster))

qplot(mkt_seg$religion,mkt_seg$sports_fandom,color=factor(kmeans$cluster)) 
qplot(mkt_seg$family,mkt_seg$parenting,color=factor(kmeans$cluster))
# cluster 1 is dominated by religion and sports_fandom, family and parenting  

qplot(mkt_seg$beauty,mkt_seg$cooking,color=factor(kmeans$cluster))
qplot(mkt_seg$cooking, mkt_seg$fashion,color=factor(kmeans$cluster))
qplot(mkt_seg$art,mkt_seg$music,color=factor(kmeans$cluster))
qplot(mkt_seg$small_business,mkt_seg$art,color=factor(kmeans$cluster))
#cluster 2 - beauty, cooking, music, art, and fashion, small business, 

qplot(mkt_seg$personal_fitness,mkt_seg$health_nutrition,color=factor(kmeans$cluster)) # cluster 3 is dominated by fitness, nutrition, and outdoors activities 

qplot(mkt_seg$politics,mkt_seg$travel,color=factor(kmeans$cluster))
qplot(mkt_seg$politics,mkt_seg$news,color=factor(kmeans$cluster))
qplot(mkt_seg$politics,mkt_seg$current_events,color=factor(kmeans$cluster))
qplot(mkt_seg$politics,mkt_seg$small_business,color=factor(kmeans$cluster))

# cluster 4 is dominated by politics, travel, news, current_event 

# cluster 5 others (adult, spam)
qplot(mkt_seg$adult,mkt_seg$spam,color=factor(kmeans$cluster))

```

From the visualisation plots, we determine that there are five clusters in the followers for our customers:
cluster 1: customers who are family-oriented and interested in religion and who are sports_fandom, family and parenting  
cluster 2: customers who are potentially young ladies who are interested in beauty, cooking, music, art, and fashion
cluster 3: customers who are likely to be body builders and interested in developing fitness and eating healthy 
cluster 4: customers who are interested in politics and current events 
cluster 5: customers who are interested in posting "adult" contents posts are who frequently spam. 

```{r}
length(which(kmeans$cluster == 1)) # 771 
length(which(kmeans$cluster == 2)) # 1706 
length(which(kmeans$cluster == 3)) # 907 
length(which(kmeans$cluster == 4)) # 4449
length(which(kmeans$cluster == 5)) # 49 

a=which(kmeans$cluster == 1)
b=which(kmeans$cluster == 2)
c=which(kmeans$cluster == 3)
d=which(kmeans$cluster == 4)
e=which(kmeans$cluster == 5)

library(scales)
cluster1 = mkt_seg[a,]
Parenting = sum(cluster1$parenting)/sum(mkt_seg$parenting)
percent(Parenting)

cluster2 = mkt_seg[b,]
Fashion = sum(cluster2$fashion)/sum(mkt_seg$fashion)
percent(Fashion)

cluster3 = mkt_seg[c,]
Fitness = sum(cluster3$personal_fitness)/sum(mkt_seg$personal_fitness)
percent(Fitness)

cluster4 = mkt_seg[d,]
Current_events = sum(cluster4$current_events)/sum(mkt_seg$current_events)
percent(Current_events)

cluster5 = mkt_seg[e,]
spam = sum(cluster5$spam)/sum(mkt_seg$spam)
percent(spam)

clusters <- c('cluster1', 'cluster2', 'cluster3', 'cluster4','cluster5') 
category <- c('Parenting', 'Fashion', 'Fitness', 'Current_events','Spam')
Percentage <- c(percent(Parenting),percent(Fashion),percent(Fitness),percent(Current_events),percent(spam))
data.frame(clusters, category, Percentage)%>% as.tbl
```


# PCA analysis 
```{r}
pc = prcomp(features, scale=TRUE)
#pc # values are eigenvector in each PC 
# summary(pc)
# PC25 explain 91% of the variance 
plot(pc,type="l")
bp = biplot(pc, scale=0, cex=0.3)

# Extract PC scores 
#str(pc)
pc$x
df <- cbind(features, pc$x[, 1:2])
#head(df)

# Plot with ggplot 
library(ggplot2)
df = data.frame(df)
ggplot(df, aes(PC1, PC2)) +  
  geom_point(shape =21, col='black')
```


```{r}
#pc$x[,1:25]
df = data.frame(pc$x[,1:25])
#df

sort(pc$rotation[,1]) 
#religion food parenting sports_fandom (top negative)

sort(pc$rotation[,2]) # sports_fandom religion parenting food (top negative)
# cooking photo_sharing fashion shopping (top positive)

```

Analyzing the first two pricipal compoents of our datasets, we cluster all the followers into three major groups. 
If we draw an y-axis at x=0, and an x-axis at y=0, we will find inactive twitter users lie on the right of the  y-axis. For all the useres on the left of the y-axis, we consider them as active users and cluster them into two major groups. Those users who lie on the second quadrant, we think they are more likely to be middle-aged people who have a family, since they tend to pay more attention about parenting, religion, and family life. While those users who lie on the second quadrant, they tend to be young ladies who focus more on beauty, shopping, fashion and, photosharing. 